A gentle swell was breaking over the roof of a subway entrance. Seagulls soared on drafts between tall buildings, their reflections warped in the hole-pocked walls of grimy glass. 

The bird shrieks and the ocean's murmur had replaced the downtown hustle years ago, but now there were other sounds as well. Soft splashes, creaking of rusty hinges. Oars, approaching.

Couple of birds dropped closer to the murky water, curious about the intrusion. Soon a boat appeared, laboriously making it around the corner of a hollowed-out bank. 

Two shady characters were sitting on the boat. Another man stood in the bow, tall and thin, as erect as the other two were slumped on their benches. The man wore a black hoodie with a cowl pulled low on his face. Weird symbols were painted all over his arms and back. If he was any good with guitar, he would be a standout at an audition for a black metal frontman.

The inquisitive seagulls lost interest after few hopeful passes above the boat. The men neither looked nor smelled like a fishing party.
 
``Crap, it's low tide,'' said the thug in a frayed baseball cap, the one with the oars.
 
``Just keep rowing, please,'' the hooded fellow said without turning back. His voice was melodic and silky, but snake bites lurked just under the smooth surface. It was quite clear who's the boss here.

The bearded mute in the back of the boat did not say anything. As always.
 
They navigated through shallows of abandoned cars and buses. It hadn't been so long since a rogue hurricane had destroyed the dams that'd protected the city for over a decade, but the vehicles were a mess already. The men took their time. No good piercing their dinghy on the heaps of rotting steel.
 
The boss guided them through the canals of the streets to a multi-storey parking garage. Decks without walls, just concrete railings and massive pillars. When they landed there, the mute scrambled over the railing. The boss threw him a rope and climbed up deftly. The last thug followed after securing the oars.
 
``Haul it up,'' the boss said. In the shade of the garage, his eyes were glowing under the hood.
 
The henchmen both thought that tying the boat by one the pillars would be just fine---
 
``No. It wouldn't,'' the boss interrupted. A wave of shiver went down the men's spines. They hated when he did that.
 
The men pulled the dinghy up and ran after the boss who was already heading up the stairs briskly.
 
The higher they were the clearer they could hear faint music. The baseball cap and the mute glanced at each other. The boss didn't seem to be perturbed though. They pressed on.

All the way up at the level just below the roof, there was a long limo with tinted windows, neatly parked across several slots. The noise was coming from it, muffled by the thick walls of the luxury car. Two dead lighting panels were pointed at the sliding door of the passenger cabin. A disconnected power line snaked on the floor.
 
The boss went and plugged the cable to a burned-out socket in the nearest wall. The panels came alive, blinking in the sluggish rhythm of the waves that swashed in the streets deep down.
 
The boss came to the front door of the limo and tapped on the roof. His men came closer. They'd had a fair share of dark adventures following the hooded guy. Still, they felt increasingly uncomfortable now, standing in the flicker of the impossible light and looking at the car that couldn't have driven up there; not with the narrow spiral of a driveway and the water everywhere around.
 
An ageless voice came from the driver's cabin: ``Is that you, Beast?''
 
``Yes. Would you mind if I opened the door?''
 
``Suit yourself.''
 
The boss opened the door. Inside, a little old man with a halo of long white hair was sitting, dressed in nondescript grey robes. He was barefoot, dirty legs propped against the dashboard. The man was smiling amiably, but his thin, deeply lined face looked impassive and stark. He was smoking a long metallic pipe that smelled like seven hells and heavens.
 
``The job's done, give or take. I demand some rest at long last,'' the boss said. ``Is he looking forward to the switchover? We've got no red carpet, but the limelight is all ready and the boys here can do a little choir thing.''

The thugs looked at each other, panicky. Especially the mute one.
 
``I'm not quite sure,'' the old man said. ``He doesn't speak to me much these days. I wouldn't bet---''
 
The rear door opened and the muted music became an explosion of fast-paced klezmer. Strong smell of frankincense wafted from the dimly lit interior. 

The boss didn't even blink, but his two thugs sprang into motion. They took their guns out and aimed at \dots a girl, dressed in something like a cheap angel costume, wings and all. She stumbled out of the car, squatted and started to relieve herself right next to them. The men shuffled nervously, not knowing where to look all of a sudden.

``Mary-Mags, dear,'' a voice croaked from the car, ``since you're out there, would you be so kind and fetch me another drink?''
 
``Jay, maybe you've had enough already?'' shouted the old driver. ``You know what we're here for, don't you?''
 
``Shut up, Pops, I'm done when I'm done! The planet looks like it will keep spinning just fine even without me, don't you think?''

The girl, Mary-Mags, looked apologetically at the driver. He just nodded, resigned. She went to the car's boot and produced a large clay jug. She spilled a little on the way back into the limo. It smelled like very old and sour wine.

The driver looked up at the boss and shrugged. 

``You see, he's been like that last couple of centuries. When he talks to me at all, he maintains he's depressed. 

``I suppose they are to blame,'' he pointed to the men who were standing next to the boss, fumbling with their guns. 

``Truth be told,'' the old man continued, ``I'm not surprised he thinks they deserve few more generations steeped in this mess. Tell me, how much did you actually have to help them to get that far?''

``Not much, lately,'' the boss admitted, grudgingly. ``That's why it's been so tiring. I can't stand the bore.''

The thugs were looking at each other once again. They felt like pawns who'd been dragged along for a party thrown by their master players, clueless as to what was going on.
 
``You think we should wait some more?'' the boss asked.
 
The old man said, dejected: ``I hate to say so, but it looks like you'll need to cope with the boredom for a little longer indeed.''
 
``Okay. I'll manage, somehow,'' the boss said. ``Try to speak some sense into him though. You used to have a pretty good bag of tricks for that.''

``I'll try. But the bag is nearly empty already.''

The boss sighed and closed the driver's door. The car disappeared at that instant. Only the lights remained, shining through a quickly thinning cloud of incense that hung in the empty air.

``Come on, boys, we're done here,'' said the boss and started back to the stairs.
 
The thugs followed, hesitantly. An unsettling conjecture of what they'd just witnessed was dawning on them. Wildly impossible, but strangely \emph{believable} all the same. They enjoyed their line of work, and even liked their boss. But now they'd started to feel like it would be really good if the guy called Jay would have changed his mind. The sooner the better. 
